An exposition on the propriety of restricted Boltzmann machines

### 2016-07-07 writing/draft.Rmd
revisiting 4x4 model with theta based on grid

#marginalized likelihood
load("data/fitted_models_adaptive_mh_trunc_distn_marginal_1.Rdata")
marginal_bad_1 <- models_bad
marginal_good_1 <- models_good
marginal_degen_1 <- models_degen

#load Jing's prior
load("data/fitted_models_distn_0.26.Rdata")
jing_bad <- models_bad
jing_good <- models_good
jing_degen <- models_degen

#truncated normal
load("data/fitted_models_adaptive_mh_trunc_distn_shrunk_jing_match.Rdata")
shrunk_jing_bad <- models_bad
shrunk_jing_good <- models_good
shrunk_jing_degen <- models_degen

>>>>

#marginalized likelihood
load("data/fitted_models_adaptive_mh_trunc_distn_marginal_1.Rdata")
marginal_bad_1 <- models_bad
marginal_good_1 <- models_good

#load Jing's prior
load("data/fitted_models_distn_0.26.Rdata")
jing_bad <- models_bad
jing_good <- models_good

#truncated normal
load("data/fitted_models_adaptive_mh_trunc_distn_shrunk_jing_match.Rdata")
shrunk_jing_bad <- models_bad
shrunk_jing_good <- models_good
